% Collin Franklin
% LaTeX Assignment 
% The percent sign indicates the start of a comment. Comments do not appear in the  
% finished document. Comments are for information only.

\documentclass{article}

\title{Example LaTeX Document}      % Enter your title between curly braces
\author{Collin Franklin}            % Enter your name between curly braces
\date{\today}                       % Enter date or\today between curly braces

\usepackage{amsmath}

% Set the beginning of a LaTeX of a LaTeX document
\begin{document}
\maketitle
\tableofcontents

\section{Introduction}

\TeX{} is a typesetting program developed by Donald Knuth \cite{knuth}. \LaTeX{} uses the \TeX{} engine
to allow author to produce professional looking documents using predefined layouts \cite{lamport}

\section{Why Learn \LaTeX{} }

For creating text documents, a basic word processor is usually sufficient. How-
ever, there are times when a \TeX{} editor is preferred. Although \LaTeX{} is not a WYDIWYG (What You See Is What You Get) environment, it does have several advantages over a traditional word processor [3]. This section outlines some of those advantages.


\subsection{Professionally Typeset Documents}

\LaTeX{} provides a consistent structure by following a predefined layout which is defined at the top of the document. For example, this document is an article. Line spacing, font size, and line length are determined by the selected layout. Document structures, such as table of contents, footnotes, and bibliographies can be automatically generated with simple commands.

\subsection{Strong Mathematical Support}

One of the best features of \LaTeX{} is the strong mathematical support. Symbols, such as $ \alpha{}, \beta{}, \lambda{} $ are easily produced with a  
\newpage

\bibliographystyle{acm}
\bibliography{reference}

\end{document}